|

### 2020-05-18 paper/Manuscript.Rmd
updae

<!-- LB: As I reader, I would prefer to hear about data sharing options before the synthetic data part (which is only relevant to those who cannot share their data). E.g. can I indicate a point in my workflow (e.g. after removing some privacy sensitive columns of my data) to share the as-raw-as-possible data ?-->
If data cannot be shared, researchers should aim to safeguard the potential for computational reproducibility and secondary analysis as much as possible. The `worcs` package uses two solutions to accomplish this goal.
The first solution is to publish a *checksum* of the original data file.
Think of a checksum as a 32-character summary of the contents of a file, or alternatively, a "one word" description of the file.
Any change to the file will result in a different checksum. 
Thus, one can use a checksum to verify the identity of a file, and ensure that its contents are unchanged.
When data cannot be shared, the risk of fraud or abuse can be mitigated by publishing a checksum for the original data, in addition to the complete analysis code.
Using the checksum to verify the identity of a private dataset, researchers can prove to an independent auditer that running the public analysis code on the private data results in the published results of their work.

>>>>

<!-- LB: As I reader, I would prefer to hear about data sharing options before the synthetic data part (which is only relevant to those who cannot share their data). E.g. can I indicate a point in my workflow (e.g. after removing some privacy sensitive columns of my data) to share the as-raw-as-possible data ?-->
If data can be shared openly, it can simply be committed it to the 'Git'
repository, along with the analysis code. This way, others can download the
entire repository and reproduce the analyses from start to finish. 
If data cannot be shared, researchers should aim to safeguard the potential for
computational reproducibility and secondary analysis as much as possible. The
`worcs` package uses two solutions to accomplish this goal.
The first solution is to publish a *checksum* of the original data file.
Think of a checksum as a 32-character summary, or as a "one word" description,
of the contents of a file.
Any change to the file will result in a different checksum. 
Thus, one can use a checksum to verify the identity of a file, and ensure that its contents are unchanged.
When data cannot be shared, the risk of fraud or abuse can be mitigated by publishing a checksum for the original data, in addition to the complete analysis code.
Using the checksum to verify the identity of a private dataset, researchers can prove to an independent auditer that running the public analysis code on the private data results in the published results of their work.
